%\chapter{What Could Go Wrong?}
\chapter{Risks}
	Having described the implementation of the prototype, it is very important to acknowledge any short-comings or dangers in the use of the final solution. As such, in this chapter the greatest risks are discussed.
	

	\section{Weak Authentication and Decryption Passwords}
		One of the most fundamental risks of using this implementation, is if the user chooses a weak password. Granted, this is a weakness that applies to \emph{everything} protected by a weak password.

		If a can be guessed easily, by known publicly available information regarding the user, or can be bruteforced in a reasonable short about of time, they are thought to be weak. Such a password would in the event of an attacker attempting to gain access, result in greater risk of leaking the \emph{actual} passwords.

		Unfortunately, preventive measures for this type of weakness, is fairly useless. Enforcing password policies is how it is often done in critical systems, but more often than not, the resulting password is chosen so it is easy to remember. As such, it is decided that this risk is \emph{completely} up to the user to avoid.

	\section{Identical Encryption and Decryption Passwords}
		In section \ref{sec:design:pseudo-zero-knowledge} on page \pageref{sec:design:pseudo-zero-knowledge} it was discussed why the design of the system requires two passwords. However, at \emph{no} point will the implementation ever actually compare these passwords. As such, it is \emph{completely} possible for the user to have identical authentication and decryption passwords.

		The risk of this, is potentially giving the server owner the ability to decrypt the stored passwords, since the authentication password \emph{is} sent to the back-end, for authentication purposes. However, this all depends on the user's \emph{choice}, and as such is not regarded as a critical risk.
	
	\section{Trusting the Server Owner}
		While the pseudo-zero-knowledge concept introduced in section \ref{sec:design:pseudo-zero-knowledge} on page \pageref{sec:design:pseudo-zero-knowledge} is intended to keep admins from reading all of the users' passwords, there is more to the story.

		The admin, whom is assumed to be the owner of the back-end, \emph{could} change the JavaScript files of the front-end, making them send all the unencrypted data back to him. 

		In \emph{theory} this could be mitigated by publishing a checksum of the bundled JavaScript file, that the front-end executes. This could then be compared, using a separate browser plugin on load, determining whether or not the file had been tampered with.

		However, there is a much more fundamental issue here: Trust. This implementation is meant to be \emph{self-hosted}. The multi-user support is intended to allow multiple users from the same small community or home, e.g. husband and wife, to share the same back-end for storing their private passwords. As such, a certain level of \emph{trust} is assumed. The pseudo-zero-knowledge ensures that the admin can not read the passwords, using information found in the implementation as originally developed. Beyond that, the users will simply have to trust the admin, that he or she will not deliberately alter the files, in order to access their passwords.

	\section{Third Party Libraries}
		As previously stated, the implementation relies on third party libraries, to perform certain functions. For instance, the Forge library is used for handling encryption in the front-end, and the Node-Argon2 library, is used for performing Argon2 password hashing in the back-end. 

		Using these libraries -- or dependencies, as they're called in the Node.js community -- enabled prototypes to be rapidly developed. However, they also introduce a risk: The implementation relies on other people's code. Recently the largest dependency manager for Node.js, npm, experienced a catastrophic event. A very basic package, \verb=left-pad= was removed from npm, due to a legal dispute between the author and a third party\cite{npm_leftpad}. This caused a chain reaction of chaos, as packages that depended on \verb=left-pad= no longer could be installed, and packages depending on those packages couldn't either -- and so forth. This is unfortunately the risk, when working with these kinds of dependencies, but it isn't even the worst.

		When depending on libraries, the developer\emph{(s)} trust that the author\emph{(s)} of the library is forthright about the content of the library. For instance, the Forge library could, for all intents and purposes, simply send every single encryption payload to a remote server. Luckily, since this \emph{is} the world of open source, the source code can be inspected, and security flaws and vulnerabilities possibly found. However, there \emph{might} still be both intentional and unintentional security risks involved with using these libraries. As such, it is the developers duty to assess the quality of \emph{any} dependency used.

	\section{Dumping the Memory}
		Unfortunately, since the implementation is run in a browser, it is not possible to implement features depending on for instance Microsoft's Data Protection Application Programming Interface \emph{(DPAPI)}, like KeePass does. As such, storing the passwords unencrypted is \emph{unfortunately} a security risk.

		There really isn't any way around this risk. For it to be shown to the user, in the browser, it needs to be decrypted. For it to be shown, it needs to be stored. Should an attacker make a dump of the process memory, he or she will \emph{unfortunately} gain access to any passwords decrypted. 

		The same is said about swap partitions and pagefiles. Unfortunately, there is a risk of clear text passwords ending up in these. It is a risk that comes with the choice of implementation. Should it have been chosen to implement native clients instead, this could possibly be circumvented. So this risk, is the price that will have to be paid, for the convenience of a web application.

		Even the encrypted passwords are somewhat at risk. For user experience purposes, the decrypted private key is kept in memory. A mechanism clearing this variable could of course be devised, but that would result in the user having to enter their decryption password \emph{every} time he or she needed to access a password -- which would result in a horrible user experience.


		%So even when removing the decrypted passwords, the encryption key for decrypting \emph{all} passwords, still resides \emph{in memory}. One could of course go about clearing this as well, but that would mean the user would have to enter the decryption password \emph{every} time he or she needed to access a password -- which would result in a horrible user experience.

		%The only redeeming thing to be said about this risk, is the fact that the implementation attempts to remove decrypted passwords again, as soon as possible. When the user changes focus from the password, its variable is overwritten. This is, however, doesn't increase the security all that much. For user experience purposes, the decrypted private key is kept in memory. So even when removing the decrypted passwords, the encryption key for decrypting \emph{all} passwords, still resides \emph{in memory}. One could of course go about clearing this as well, but that would mean the user would have to enter the decryption password \emph{every} time he or she needed to access a password -- which would result in a horrible user experience.

		All in all, this risk is unfortunately unavoidable. It is simply the price paid for the convenience.
	
	\section{Loss of Data in the Database}
		As much as we wish they were, harddrives, flash cards, and USB sticks are fallible. Drive failures \emph{can} -- and eventually \emph{will} -- happen. Unfortunately, not all users will run with a setup supporting parity checks. As such, backing up the database every so often is very much \emph{encouraged}. While this will \emph{not} completely mitigate the threat of data loss, it minimizes the damage done in such an event.

		Backing up the database can easily be done with a cronjob \emph{(or similar)}.

	\section{Leaking the Token}
		In section \ref{sec:design:jwt} on page \pageref{sec:design:jwt} it was decided that the implementation will be using JWT's to handle API authentication. What was \emph{not} discussed, was the security impact this would have.

		When JWTs are used, commonly there is an expiration time set. At the time of this writing, that timer is set to 24 hours, meaning that 24 hours after issuing, the token is no longer valid. As such, after the token is expired the user will need to re-authenticate to access the back-end again.

		However, that also means that should this token fall into the hands of the attacker, he or she will have access to the user's data for 24 hours. This would allow an attacker to change and delete passwords at will, but since password encryption and decryption happens in the browser, he or she will \emph{not} have direct access to the passwords. Avoiding the loss of passwords, can be somewhat mitigated, by backing up the database, as described in the previous section.

		Obtaining these tokens commonly happen through either Cross-Site Request Forgery \emph{(CSRF)} or Cross-Site Scripting \emph{(XSS)}. While there definitely could be security vulnerabilities not found at this point, it is believed that no such exists. Additionally, it is not possible to intercept the token in transit, due to HTTPS being enforced at \emph{all} times.

		As such, the risk of the token being compromised, is relatively low.

		%Another option is to allow for token revocation. This would entail storing the token in the database, allowing the user to revoke tokens at any point in time.


	\section{Forgetting the Password}
		One of the more unfortunate ``issues'' with the implementation, is the lack of account recovery. The authentication password can, \emph{of course}, be reset. But the decryption password can \emph{not} be reset -- for good reasons. As such, if the user forgets his or her decryption password, \emph{nothing} can be done.

		Should this situation arise, it would be unfortunate. But there is nothing that can be done to remedy this risk, that would not lower the overall security of the system. As such, it is deemed a necessary risk.

	\section{Summing Things Up}
		In the previous sections various risks of running the system has been introduced. These range from trusting the owner of the setup, to depending on third party libraries.




		Taken all the risks into consideration, it is still deemed better to deploy the solution as is, rather than trusting remote services with ones password data.
